%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Designated campus observer of the Department of Astronomy and Astrophysics}
    {Campus observer}
    {Toronto, Canada}
    {Sep. 2018 -- Apr. 2019}
    {
      \begin{cvitems}
        \item {Supported and maintained campus telescopes and related hardware}
        \item {Instructed undergraduate students in modern telescope systems}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Web developer at system-sounds.com}
    {SYSTEM Sounds}
    {Toronto, Canada}
    {Jul. 2017 -- May 2018}
    {
      \begin{cvitems}
        \item {Web application (HTML5/CSS3/JS) of astro-musical systems}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Program coordinator (Astronomy)}
    {Science Unlimited}
    {Toronto, Canada}
    {Jan.--Jul. 2016}
    {
      \begin{cvitems}
        \item {Created and ran the astronomy module for a summer camp for high school students hosted by the Department of Physics at the University of Toronto}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Researcher for the Wide Integral-Field Infrared Spectrograph (WIFIS) project}
    {Research Assistant (Prof.\@ Dae-Sik Moon)}
    {Toronto, Canada}
    {May--Aug. 2015}
    {
      \begin{cvitems}
        \item {Built and developed the motor control system in the main telescope control program}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Developer}
    {Centre de Recherche sur l'Interpr\'{e}tation au Clavecin}
    {Montr\'{e}al, Canada}
    {May 2014 -- Apr. 2015}
    {
      \begin{cvitems}
        \item {Developed the algorithm for automatic figured bass realization in a robotic score-following harpsichord}
        \item {Conference presentation at the International Conference of the Historical Keyboard Society of North America 2015}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Researcher at the Geophysics Laboratory}
    {Research Assistant (Prof.\@ Sabine Stanley)}
    {Toronto, Canada}
    {May 2010 -- Aug. 2013}
    {
      \begin{cvitems}
        \item {Investigated magnetic instabilities in rapidly rotating geometries (2012--2013) and the Martian paleomagnetic field and paleopoles (2010--2012)}
        \item {Conference presentation at the EPSC--DPS Joint Meeting 2011}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Recipient of the NSERC undergraduate student research award (USRA)}
    {Undergraduate Researcher (Prof.\@ Christopher Matzner)}
    {Toronto, Canada}
    {Sep. 2010 -- Aug. 2011}
    {
      \begin{cvitems}
        \item {Investigated collapsar accretion disks around spinning black holes}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
